Paper 1: Vitis

### 2018-02-08 Paper-1-Vitis.Rmd
Commit from RStudio

>>>>

# Principal Components Analysis (PCA)

```{r}
library(pcaMethods)
excel_sheets("R_DiLP_Vitis_all_added.xlsx")
```

First, we applied a PCA to *Vitis acerifolia*.
```{r}
ac_ln <- read_excel("R_DiLP_Vitis_all_added.xlsx", sheet = "acerifolia.all.ln")
ac_ln_mat <- data.matrix(ac_ln, rownames.force = NA)
ac_ln_fixed <- ac_ln_mat[,-(1:3)]
ac_ln_fixed[ac_ln_fixed == 0] <- NA
pca_ac_all <- pca(ac_ln_fixed, method = "nipals", center = TRUE, nPcs = 5)
summary(pca_ac_all)
loadings(pca_ac_all)
scores_pca_ac <- scores(pca_ac_all)
scores_pca_ac_df <- as.data.frame(scores_pca_ac)
str(scores_pca_ac_df)
#ggplot(scores_pca_ac_df, aes(x = PC1, y = PC2, label = rownames(scores_pca_ac_df))) +
  #geom_col(x = PC1, y = PC2) +
  #ggtitle("PCA plot of Vitis acerifolia")
#attach row names
```
